Dynamic Anomaly Detection for Collective Data via Statistical Distance

### 2017-09-28 Paper/Template/paper.tex
Using template for paper

\documentclass[a4paper]{IEEEtran}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{paper}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
\title{Dynamic Anomaly Detection for Collective Data Via Statistical Distance}
%
\author{%
	% author names are typeset in 11pt, which is the default size in the author block
	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
	% add some space between author names and affils
	\vspace{1.6mm}\\
	\fontsize{10}{10}\selectfont\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separate superscript on following line from affiliation using narrow space
	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
	No.800 Dongchuan Rd. Shanghai, 200240, China\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	%
	% 20080211 CAUSAL PRODUCTIONS
	% in the following email addresses, separate the superscript from the email address 
	% using a narrow space \,
	% the reason is that Acrobat Reader has an option to auto-detect urls and email
	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
	% in the email address and corrupts it.
	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{1}$\,solftwarewry@sjtu.edu.cn\\
	$^{3}$\,li.g@sjtu.edu.cn%
	% add some space between email and affil
	\vspace{1.2mm}\\
	\fontsize{10}{10}\selectfont\rmfamily\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separated superscript on following line from affiliation using narrow space \,
	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	% 20080211 CAUSAL PRODUCTIONS
	% removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{2}$\,daniel.sun@data61.csiro.au
}

\begin{document}
	\maketitle

	\begin{abstract}
		Hackers can infiltrate networks and find their way into databases and software systems. Not only
		can they steal chunks of data and hold them for ransom, but
		also alter key information contained in those systems, setting up
		traps hard to discover and causing damages unlikely to recover.
		Although altering single record may not oblige correct value scope such that it is hard to detect, the change, especially to a subset of data, can be observed and detected in a collective
		scale. In this paper, we present a collective anomaly
		detection technique based on statistical distance. The technique
		extracts distribution similarities among data collections, and then uses the statistical distance to detect
		collective anomalies. In order to adapt to data dynamics, our technique continuously evaluates 
		metrics as evolving features. Aiming at broad generalisation, this
		technique can replace several components of our solution to further improve the
		performance of detection for various scenarios. To illustrate details of the technique
		and explore its efficiency, we case-studied a real
		world problem of click farming detection against malicious online
		sellers. The evaluation shows that the technique maps normal
		and anomalous data collections into two distinct clusters by yielding
		efficient classifiers. Those classifiers are sensitive sufficiently to
		a much smaller magnitude of data alerting, compared with real
		world malicious behaviours--that is--it is applicable in the real world.

		%Hackers can infiltrate networks via any attack vector, find their way into databases and applications. Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover. Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
		%In this paper, we present a dynamic collective anomaly detection technique based on statistical distance. The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies. It dynamically calculate metrics which is adaptive to the slightly evolving features. This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
		%To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers. The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers. And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
	\end{abstract}

	\section{Introduction}
		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability. Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics} and the growing speed is doubling every two years.
		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
		%Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
		%
		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.

		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years. And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}. System configuration problems, as a matter of fact, also draw scratches to the messy picture. They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

		Those data anomalies may arise due to both internal and external reasons with respect to a certain system. On one hand, components inside the system may generate problematic source data. For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\autocite{rassam2014adaptive}. Data packages will be lost if sensor nodes fail to connect to network or some sensor hub goes down~\autocite{herodotou2014scalable}. Also, human operators act as a heavily vulnerable part to bugs and mistakes. Some insiders even deliberately modify system configurations for malicious compromises~\autocite{schuster2015vc3}. A study~\autocite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.

		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
		% Take an example of Apache Hadoop, Hadoop's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}. As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats. Data flows can be intercepted and modified; services can also be altered and blocked~\autocite{huang2014denial}. Although there are several frameworks(e.g. Kerberos, Sentry, Knox etc.) and algorithms providing basic protection~\autocite{zheng2017towards,sikdar2017spatio,xu2016high,yu2015enhancing,cohen2014towards}, clever attackers can always bypass the barriers and sneak into the core of data pipelines. Several approaches are developed as sentinels to detect probable infiltrations. However, these approaches are not able to detect corrupted data under carefully planned manipulations. Nor can they figure out the exact reasons and recover the original records. 
		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system. In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
		% To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still in demand by industry and academia.

		%\begin{figure}[!t]
		%	\includegraphics[width=\linewidth]{fig/HadoopSecurity}
		%	\caption{Security Issues of Hadoop Clusters}
		%	\label{fig:hadoop-security}
		%\end{figure}

		However, from the aspect of data itself, we can still detect malicious data manipulation behaviours.
		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution. With the reshaping measurable, we can enclose data collections with similar distribution forms inside the same cluster and filter out those strange shaped ones. In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions. Comparing with a estimated ground truth, each data collection can be mapped to a single real number within a definite interval. Then a gaussian classifier can be applied to detect outliers derived from manipulated data. To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence. And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
		%For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales. Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day. The curve for cheated data is emulated according to a popular method for click farming. It can be observed that there exists clearly a gap between these two distributions. 		
		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.

		The rest of the paper is organised as follow: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem. Section~\ref{sec:preliminaries} introduces statistical distance. Details of the technique are proposed in section~\ref{sec:algorithm-details}. Section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm. And all contents are concluded in section~\ref{sec:conclusion}.

@@

			Prevalent anomalies can be classified into \textit{Point Anomalies}, \textit{Contextual(or Conditional) Anomalies} and \textit{Collective Anomalies}. Point anomalies refers to an individual data instance that is considered anomalous with respect to others. But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly. If a group of related data(e.g. a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g. the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.

@@

		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
			Since the establishment of Taobao in 2003, the online business platform has been growing from the rookies in the market to the No.1 service provider in B2B and B2C markets, possessing a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}. Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products. Under the super-pressure from massive competition, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.

			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of buyer accounts to create fake transaction records and give high remarks on products. Professional click farmers are usually well organized groups or companies containing thousands of people. Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.

@@

			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect. For normal sellers, their customers are usually similar since choices of products are seldom changed. Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable. No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution. To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records(see section~\ref{sec:exp-methodology}) and emulated the circumstances if it had been click farmed. Figure~\ref{fig:example-ecdf} shows the difference between one daily distribution with and without click farming.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
				\label{fig:example-ecdf}
			\end{figure}

			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		% This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem. Then a concrete point anomaly detection classifier can be used to find out the cheaters.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $S$ be a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
		\end{equation}

@@

		\begin{enumerate}
			\item $D(P||Q) \ge 0, \forall P, Q \in S$
			\item $D(P||Q) = 0$, if and only if $P=Q$
		\end{enumerate}

		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$. But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$. There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
		%Some of them provides better properties which brings conveniences to the design and implementation of our approach. 
		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence which is derived from Kullback-Leibler as the measurement.

		\subsubsection{Kullback-Leibler Divergence}
		Let $P,Q$ be discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:

@@

		\subsubsection{Jensen-Shannon Divergence}
		Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data. For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data(e.g. Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm. Main idea of the solution is simple. But there are several difficulties to be solved in the design and implementation of the technique:

@@

		\ref{sec:alg-basic} answers the first question and introduces a basic framework of our technique. The second question is studied in~\ref{sec:alg-histogram}. \ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error. And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.

		\subsection{Divergence-Based Collective Anomaly Detection}\label{sec:alg-basic}
			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph that each node denotes one certain collection and each edge refers to the divergence of two data collections. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous ones do not compose a large proportion of all points. However the procedure will be too complicated to work out with large amounts of instances.

			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones. Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several already known correct distributions. Then the real distribution can be estimated by averaging all distributions in $\mathbb{E}$. This process is similar to the parameter estimation within a certain sample set. Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $\mathbb{E}$, yielding absolute distances.

			Fig.~\ref{fig:raw-hist-1st} and~\ref{fig:raw-hist-2nd} in section~\ref{sec:exp-raw} show the result of the above process. Red dots refer to the distances calculated from normal transaction data collections, blue and green ones are from click farmed collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones are distributed around a larger distance value. Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points. The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}:

@@

			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies. Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$, it is not viable for classification. Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large. For example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $P'(1) = \frac{1}{6}, P'(2) = \frac{1}{3}, P'(3) = \frac{1}{2}$, then $JSD(P||P') \approx 0.023$ and $JSD(P, P, P, P') \approx 0.017$.

>>>>

% IEEE Paper Template for US-LETTER Page Size (V1)
% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
% Permission is granted to distribute and revise this file provided that
% this header remains intact.
%
% REVISION HISTORY
% 20080211 changed some space characters in the title-author block
%
\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,amsfonts,epsfig}
\usepackage{graphicx}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
%
\title{Dynamic Anomaly Detection for Collective Data via Statistical Distance}
%
\author{%
	% author names are typeset in 11pt, which is the default size in the author block
	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
	% add some space between author names and affils
	\vspace{1.6mm}\\
	\fontsize{10}{10}\selectfont\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separate superscript on following line from affiliation using narrow space
	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
	No.800 Dongchuan Rd. Shanghai, 200240, China\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	%
	% 20080211 CAUSAL PRODUCTIONS
	% in the following email addresses, separate the superscript from the email address 
	% using a narrow space \,
	% the reason is that Acrobat Reader has an option to auto-detect urls and email
	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
	% in the email address and corrupts it.
	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{1}$\,solftwarewry@sjtu.edu.cn\\
	$^{3}$\,li.g@sjtu.edu.cn%
	% add some space between email and affil
	\vspace{1.2mm}\\
	\fontsize{10}{10}\selectfont\rmfamily\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separated superscript on following line from affiliation using narrow space \,
	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	% 20080211 CAUSAL PRODUCTIONS
	% removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{2}$\,daniel.sun@data61.csiro.au
}

%
\begin{document}
\maketitle
%
	\begin{abstract} 
		Hackers can infiltrate networks and find their way into databases and software systems. Not only
		can they steal chunks of data and hold them for ransom, but
		also alter key information contained in those systems, setting up
		traps hard to discover and causing damages unlikely to recover.
		Although altering single record may not oblige correct value scope such that it is hard to detect, the change, especially to a subset of data, can be observed and detected in a collective
		scale. In this paper, we present a collective anomaly
		detection technique based on statistical distance. The technique
		extracts distribution similarities among data collections, and then uses the statistical distance to detect
		collective anomalies. In order to adapt to data dynamics, our technique continuously evaluates 
		metrics as evolving features. Aiming at broad generalisation, this
		technique can replace several components of our solution to further improve the
		performance of detection for various scenarios. To illustrate details of the technique
		and explore its efficiency, we case-studied a real
		world problem of click farming detection against malicious online
		sellers. The evaluation shows that the technique maps normal
		and anomalous data collections into two distinct clusters by yielding
		efficient classifiers. Those classifiers are sensitive sufficiently to
		a much smaller magnitude of data alerting, compared with real
		world malicious behaviours--that is--it is applicable in the real world. 
	\end{abstract}

% NOTE keywords are not used for conference papers so do not populate them
% \begin{keywords}
% keyword-1, keyword-2, keyword-3
% \end{keywords}
%
	\section{Introduction}
		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability. Currently, there are totally 2.7ZB data in the digital universe~\cite{bigDataStatistics} and the growing speed is doubling every two years.
		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those occurred at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years. And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}. System configuration problems, as a matter of fact, are also responsible for the disturbing situation. They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\cite{saha2014data}. Those data anomalies may arise due to both internal and external reasons with respect to a certain system. On one hand, components inside the system may generate problematic source data. For example, in a sensor network, some sensors may generate erroneous data when it experiences power failure or other extreme conditions~\cite{rassam2014adaptive}. Data packages will be lost if sensor nodes fail to connect to network or some sensor hubs break down~\cite{herodotou2014scalable}. Also, human operators act as a heavily vulnerable part to bugs and mistakes. Malicious insiders even deliberately modify system configurations for fatal compromises~\cite{schuster2015vc3}. A study~\cite{humanError} found that 65\% of organizations state that human errors are the main  cause of data problems.

		On the other hand, data manipulation~\cite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system. In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.

		However, from the aspect of data itself, we can still detect malicious data manipulation behaviours.
		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution. With the reshaping measurable, we can enclose data collections with similar distribution patterns inside the same cluster and filter out those strange shaped ones. In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions. Comparing with a estimated ground truth, each data collection can be mapped into a single real number within a definite interval. Then a gaussian classifier can be applied to detect outliers derived from manipulated data. To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence. And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.

		The rest of the paper is organised as follows: Section~\ref{sec:related-work} states related works on data anomaly detection and describes a real world problem. Section~\ref{sec:preliminaries} introduces statistical distance. Details of the technique are proposed in section~\ref{sec:algorithm-details}. Then section~\ref{sec:evaluation} presents evaluation results and further findings of the algorithm. Finally, all contents are concluded and discussed in section~\ref{sec:conclusion}.

@@

			Prevalent anomalies can be classified into \textit{point anomalies}, \textit{contextual(or conditional) anomalies} and \textit{collective anomalies}. Point anomaly refers to an individual data instance that is considered anomalous with respect to others. But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly. If a group of related data instances(e.g. a segment of sequence) is anomalous with respect to other groups in the data set(e.g. the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.

@@

		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
			Since the establishment of Taobao in 2003, its online business platform has been growing from a follower in the market to the No.1 service provider in B2B and B2C markets, possessing a market share of 50.6\% to 56.2\% in China by 2016~\cite{iresearch2016b2c}. Currently, there are more than 9.4 million sellers in Taobao, providing more than 1 billion different products. Under the super-pressure caused by massive competitors, most of the sellers choose to use some cheating techniques to raise reputation and product sale volumes, then improve rankings in search lists.

			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of dedicated customer accounts to create fake transaction records and give high remarks on products. Professional click farmers are usually well organized groups or companies containing thousands of people. Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.

@@

			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect. For normal sellers, their customers are usually similar since choices of products are seldom changed. Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable. No matter how much alike between honest users and robots or the employed workers, the fake transaction records will always cause a bias or distortion of the original transaction distribution. To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records and emulated the circumstances if it had been click farmed(see section~\ref{sec:exp-methodology}). Fig.~\ref{fig:example-ecdf} shows the difference between normal and click farmed distributions of one day in the data set.
			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleCDF.png}
				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
				\label{fig:example-ecdf}
			\end{figure}

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $\mathbb{S}$ be a space of probability distributions, then a divergence is a function from $\mathbb{S}$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
		\end{equation}

@@

		\begin{enumerate}
			\item $D(P||Q) \ge 0, \forall P, Q \in \mathbb{S}$
			\item $D(P||Q) = 0$, if and only if $P=Q$
		\end{enumerate}

		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$. But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$. There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence, which is derived from Kullback-Leibler divergence, as the measurement.

		\subsection{Kullback-Leibler Divergence}
			Let $P,Q$ be discrete probability distributions, $Q(i)=0$ implies $P(i)=0$ for $\forall i$, the \textit{Kullback-Leibler Divergence} from $Q$ to $P$ is defined to be:

@@

		\subsection{Jensen-Shannon Divergence}
			Let $P,Q$ be discrete probability distributions, \textit{Jensen-Shannon Divergence} between $P$ and $Q$ is defined to be:

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data. For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data(e.g. Fig.~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm. Main idea of the solution is simple. But there are several difficulties to be solved in the specific design and implementation of the technique:

@@

		These questions are addressed in the following subsections correspondingly.
		\ref{sec:alg-basic} answers the first question and introduces a basic framework of our technique. The second question is studied in~\ref{sec:alg-histogram}. Then \ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error. And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.

		\subsection{Divergence-Based Collective Anomaly Detection}\label{sec:alg-basic}
			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the divergence between two connected nodes. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous nodes do not compose a large proportion. However the procedure will be too complicated to work out with large amounts of data collections.

			Otherwise we need a frame of reference that provides absolute coordinates rather than the relative ones. Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several correct distributions that have already been given. Then the real distribution can be estimated by averaging all distributions in $\mathbb{E}$. This process is similar to the parameter estimation within a certain sample set. Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside and outside $\mathbb{E}$, yielding absolute distances.

			Fig.~\ref{fig:raw-overview} in section~\ref{sec:exp-raw} demonstrates the result of the above process. Red dots refer to the distances calculated from normal data collections, blue and green ones are from click farmed data collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value. Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points. The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}.

@@

			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies. JSD here cannot be replaced by KLD since entries in $P'$ are not necessarily defined in $M$. Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$, it is not viable for classification. Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large. For example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $P'(1) = \frac{1}{6}, P'(2) = \frac{1}{3}, P'(3) = \frac{1}{2}$, then $JSD(P||P') \approx 0.023$ and $JSD(P, P, P, P') \approx 0.017$.

			According to the property of statistical divergence, we can infer that the true distribution of JSDs calculated form normal data collections are close to but not exactly a gaussian distribution $N(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities. Therefore, $\mu$ should be slightly larger than zero. The reason why $\mu$ cannot be exactly zero is hidden in line~\ref{line:population-estimation}.
			For $\mu = 0$ if and only if $J_i = 0$ for $\forall i = 1, \dots, n$, which is equivalent to $P_i = P_j$ for $\forall i, j = 1, \dots, n$. And, $\lim_{n\rightarrow+\infty}P(P_i = P_j,\forall i, j = 1, \dots, n)=0$. Thus it is highly unlikely for real world data sets to have $u=0$.

		\subsection{Distribution Histogram}\label{sec:alg-histogram}
			Not all data collections can be assumed subject to known distributions. Parameter approximation will probably lead to errors far beyond our expectation. For example, the distribution of vehicle volume in the highway may be of the shape of two connected gaussian curves and does not correspond to any of the prevalent distribution models. Few assumption of parameters can be made in advance on such data. For the sake of generality, non-parametric estimation should be applied.

			Surely, the kernel density estimation approaches will give a smooth, continuous distribution curve on any sampled data. But the computational cost will be much higher than applying a coarse histogram approximation.
			Moreover, even if we applied a distribution model upon a collection of sampled data, yielding more accurate results, the computation of divergence will be much more complex on continuous functions than discrete distributions.
